MSF_Groupwork-NBA_shotlog

### 2016-10-12 MSFGroupwork-NBAHotHand.Rmd
Rest days

restdays<-cast(df1, DATE+ HOME_TEAM + AWAY_TEAM + WINNER ~ FGM)
```

>>>>

restdays<-cast(df1, DATE+ HOME_TEAM + AWAY_TEAM + WINNER ~ FGM)

#this code is supposed to produce a list of dates when teams play at HOME in DATES column. for some reason it is not working.

for (i in aa3$TEAM) {
  for (j in 1:nrow(restdays)) {
    aa3$DATES<- as.list(aa3$DATES)
    if (restdays$HOME_TEAM[j]==i) aa3$DATES[aa3$TEAM==i]<- c(aa3$DATES[aa3$TEAM==i], restdays$DATE[j])}}
